Replacing standard galaxy profiles with \\ mixtures of Gaussians

### 2012-10-20 documents/mixtures/mixture_models.tex
notes to self
notes re convolution

% to-do
% -----
% - URGENT: badness has another term in it -- the regularization term
% - add introduction comments about *why* people fit these profiles -- an opportunity to get on the soapbox
% - make figures showing use of the models in a real situation
% - does the Lupton paper give the profiles, or should we cite the code directly?
% - send to Jim Bosch and Kevin Bundy for comments

@@

\clearpage
\begin{figure}
% DSTN:  This should be a 3-across by 2-down figure,
\caption{Demonstration of use of the profiles, or the implicit
  generative model in this \documentname.  \textsl{top-left:} The
  circular dimensionless $M^{\luv}=8$ mixture-of-Gaussian
  approximation to the luv profile, represented on a very fine pixel
  grid. \textsl{top-middle:} The ellipse representing the non-trivial
  affine transformation to be applied to the circular, dimensionless
  profile.  \textsl{top-right:} The sheared profile.
  \textsl{bottom-left:} A $K=3$ mixture-of-Gaussian model of the
  pixel-convolved point-spread function, represented on the very fine
  pixel grid.  \textsl{bottom-middle:} The sheared profile convolved
  with the PSF, represented on the very fine pixel grid.
  \textsl{bottom-right:} The sheared luv convolved with the PSF, but
  now shown on a realistic pixel grid.  Because by assumption the PSF
  is a pixel-convolved PSF, the representation on the realistic grid
  is found simply by interpolating the convolved high-resolution
  model.\label{fig:example}}
\end{figure}

>>>>

% to-do
% -----
% - URGENT: badness has another term in it -- the regularization term
% - DSTN: make figures showing use of the models in a real situation; see last figure
% - does the Lupton paper give the profiles, or should we cite the code directly?
% - make sure the technical issues about convolution and interpolation don't exist *only* in the figure caption
% - send to Jim Bosch and Kevin Bundy for comments

@@

\clearpage
\begin{figure}
% DSTN:  This should be a 3-across by 2-down figure,
\caption{Demonstration of use of the profiles, or the implicit
  generative model in this \documentname.  \textsl{top-left:} The
  circular dimensionless $M^{\luv}=8$ mixture-of-Gaussian
  approximation to the luv profile, represented on a very fine pixel
  grid. \textsl{top-middle:} The ellipse representing the non-trivial
  affine transformation to be applied to the circular, dimensionless
  profile.  \textsl{top-right:} The sheared profile.
  \textsl{bottom-left:} A $K=3$ mixture-of-Gaussian model of the
  pixel-convolved point-spread function, represented on the very fine
  pixel grid.  \textsl{bottom-middle:} The sheared profile convolved
  with the PSF, represented on the very fine pixel grid.
  \textsl{bottom-right:} The sheared luv convolved with the PSF, but
  now shown on a realistic pixel grid.  Because by assumption the PSF
  is a pixel-convolved PSF, the representation on the realistic grid
  is found simply by interpolating to the pixel centers the convolved
  high-resolution model.\label{fig:example}}
\end{figure}
